Type Refinements for the Working Class

### 2015-11-22 paper.tex
rename "logical framework" to "judgmental framework"

\section{The Ambient Logical Framework}
\label{section:ambient-lf}

@@

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic logical framework equipped with higher-order judgments. A
judgment is always defined using a \emph{meaning explanation}, which is a
specification of the conditions under which it may be asserted (sc.\ its
evidence) \cite{martin-lof:1996}.

\paragraph{Renaming convention} Because the evidence of a judgment will often
contain symbols $u,v,\dots$ we informally adopt the convention that the
evidence of a judgment shall always be subject to fresh renamings of its free
symbols (i.e.\ the validity of a judgment shall not depend on choice of names).
This apparatus is developed formally in Appendix~\ref{appendix:lf}, where the
logical framework is cast as a topos of covariant presheaves on symbol contexts
$\SCtx$.

@@

\newpage
\begin{appendices}
\section{Formal Definition of the Logical Framework}
\label{appendix:lf}

As noted earlier, we must be cautious in the definitions of both atomic and
higher-order judgments that their evidence shall always respect the
\emph{renaming convention}. We do so explicitly in this appendix by developing
our logical framework as a presheaf topos over symbol contexts.

>>>>

\section{The Ambient Judgmental Framework}
\label{section:ambient-lf}

@@

For any abt signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we can
deploy a generic judgmental framework equipped with higher-order judgments. A
judgment is always defined using a \emph{meaning explanation}, which is a
specification of the conditions under which it may be asserted (sc.\ its
evidence) \cite{martin-lof:1996}.

\paragraph{Renaming convention} Because the evidence of a judgment will often
contain symbols $u,v,\dots$ we informally adopt the convention that the
evidence of a judgment shall always be subject to fresh renamings of its free
symbols (i.e.\ the validity of a judgment shall not depend on choice of names).
This apparatus is developed formally in Appendix~\ref{appendix:lf}, where the
judgmental framework is cast as a topos of covariant presheaves on symbol contexts
$\SCtx$.

@@

\newpage
\begin{appendices}
\section{Formal Definition of the Judgmental Framework}
\label{appendix:lf}

As noted earlier, we must be cautious in the definitions of both atomic and
higher-order judgments that their evidence shall always respect the
\emph{renaming convention}. We do so explicitly in this appendix by developing
our judgmental framework as a presheaf topos over symbol contexts.
